\LARGE \bf Detection of design pattern : A systematic mapping study

### 2015-12-31 article/main.tex
modified:   article/main.tex abstract

% Place holder

Lorem ipsum dolor sit amet, consectetur adipiscing elit. In pulvinar dui eget dignissim congue. Aenean interdum orci arcu, non varius nibh condimentum eu. Ut eget purus et purus pharetra egestas. Sed nec convallis lorem. Mauris fringilla velit est, elementum tincidunt lorem hendrerit ac. Vivamus et lorem nisi. Maecenas interdum diam id turpis aliquet lacinia.

Morbi rutrum tortor volutpat lacus lobortis interdum. Nam at mauris tristique, vulputate tortor non, egestas ex. Ut mauris libero, egestas at lacus sit amet, volutpat volutpat sapien. Quisque aliquet diam maximus lorem laoreet accumsan. Integer eleifend magna at nunc dapibus bibendum. Nam sagittis velit quis neque rhoncus, eget venenatis ante suscipit. Cras condimentum quam justo, quis pharetra nisi porta at. Sed sed ultricies dui. Sed id facilisis metus.

Maecenas feugiat augue purus, id interdum tellus sagittis at. Donec a orci sem. Aenean non elit maximus, fermentum odio et, mattis neque. Sed interdum in odio at egestas. Proin vel mi at elit congue lacinia et eu lectus. Praesent at rhoncus ante. Sed pulvinar tortor quis congue sagittis. Quisque tortor mi, semper vel rhoncus eu, sollicitudin et nibh.

>>>>

% Place holder
Design patterns are important because they help solving recurring design problems in software engineering. The identification of those patterns can be helpful to maintain and understand the code especially in large systems. Interest in design patterns detection has grown in the last decade.Despite the huge interest given to design patterns detection, there is no reliable or formal method for this matter.
We conducted a systematic mapping study on design patterns detection by querying multiple sources to get articles that are relevant to our study. 403 articles between 2000 and 2015 were considered.
The main purpose of the study is to know which methods and techniques are used to detect design patterns.
The result help us understand how those techniques work and which type of pattern is detected the most.
